---
title: "3 Kuang Rubrics"
author: "Jason Lu", "Jung Hwa Yeom", "Jinzhe Zhang", "Xiaozhou Lu"
date: "4/12/2021"
output: pdf_document
---

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(arm)
```

### Initializing dataset and cleaning names
```{r}
data1 <- read_excel("Student Record Clean Adminstration 1 No missing data.xlsx")
# head(data1)
data1$session <- "First"
names(data1) <- c("Student_ID","June_2019","Sept_2019","Average_2019","TchrTotal","TchrOne","TchrTwo","TchrThree","SelfTotal","SelfOne","SelfTwo","SelfThree","Session")
```

### Correlation method
```{r}
# ++++++++++++++++++++++++++++
# flattenCorrMatrix
# ++++++++++++++++++++++++++++
# cormat : matrix of the correlation coefficients
# pmat : matrix of the correlation p-values
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
library(Hmisc)
res2<-rcorr(as.matrix(data1[,2:12]))
View(flattenCorrMatrix(res2$r, res2$P))    # gives every variable's correlation against each other
```

```{r}
# Insignificant correlations are leaved blank
library(corrplot)
corrplot((res2$r),type="upper", order="hclust", 
         p.mat = res2$P, sig.level = 0.01, insig = "blank")
```

# scatterplot EDA
```{r}
data_a <- data.frame(data1)
tchr <- ggplot(data_a, aes(x=Student_ID, y=TchrTotal, color="Teacher Total"))+ geom_point(color="blue")
stu <- ggplot(data_a, aes(x=Student_ID, y=SelfTotal, color="Self Total"))+ geom_point(color="red")

plot(x=data_a$Student_ID, y=data_a$TchrTotal, col="blue", pch=19)
points(data1$SelfTotal, col="red", pch=19)

# scatterplot for SelfTotal vs. TchrTotal
plot(data1$SelfTotal, data1$TchrTotal, pch=19, xlab="Self Total", ylab="Teacher Total", main="Self Total vs. Teacher Total")
```

# Quasibinomial model
```{r}
quasibm <- glm(cbind(SelfTotal, 25-SelfTotal)~TchrTotal + Average_2019, data=data1, family=quasibinomial)
quasibm
summary(quasibm)
plot(quasibm)
# binned residual plot
binnedplot(fitted(quasibm),resid(quasibm))
```

```{r}
# quasibinomial for selfone
bm1 <- glm(cbind(SelfOne, 10-SelfOne)~TchrTotal + Average_2019, data=data1, family=quasibinomial)
bm1
summary(bm1)
plot(bm1)
# binned residual plot
binnedplot(fitted(bm1),resid(bm1))
```

```{r}
# quasibinomial for selftwo
bm2 <- glm(cbind(SelfTwo, 10-SelfTwo)~TchrTotal + Average_2019, data=data1, family=quasibinomial)
bm2
summary(bm2)
plot(bm2)
# binned residual plot
binnedplot(fitted(bm2),resid(bm2))
```

```{r}
# quasibinomial for selfthree
bm3 <- glm(cbind(SelfThree, 5-SelfThree)~TchrTotal + Average_2019, data=data1, family=quasibinomial)
bm3
summary(bm3)
plot(bm3)
# binned residual plot
binnedplot(fitted(bm3),resid(bm3))
```
### References:
http://www.sthda.com/english/wiki/correlation-matrix-a-quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-using-r-software

http://www.sthda.com/english/articles/39-regression-model-diagnostics/161-linear-regression-assumptions-and-diagnostics-in-r-essentials/#regression-assumptions

http://www.john-ros.com/Rcourse/lme.html




### Not used: EDA and initial modeling
creating dataset for students who took exam twice
```{r}
data2 <- read_excel("Student Record Clean Adminstration 2 No missing data.xlsx")
data2$session <- "Second"
names(data2) <- c("Student_ID","June_2019","Sept_2019","Average_2019","TchrTotal","TchrOne","TchrTwo","TchrThree","SelfTotal","SelfOne","SelfTwo","SelfThree","Session")

common_students <- inner_join(data1,data2,by="Student_ID")[,1]
common_students <- as.numeric(unlist(common_students))

dataS1 <- data1[1,]
for(i in 1:length(common_students)){
  dataS1[i,] <- data1[which(data1$Student_ID == common_students[i]),]
}

data_paired <- rbind(dataS1,data2)
```

```{r}
colnames(data1)
pairs(data1[,-c(1,2,3,6,7,8,10,11,12,13)])
```

 Initial Model: Fit for data1 and regression assumptions
```{r}
fit <- lm(SelfTotal ~ Average_2019 + TchrTotal, data=data1)
summary(fit)
par(mfrow = c(2, 2))
plot(fit)
```
Assumptions (4): 
Linearity of data, Constant Variance of residuals (1, Residuals vs Fitted); OK
Normality of residuals (2, Normal Q-Q); OK
Independence of residual error

 ***glm w/ binomial family, different links
```{r}
# Student Self Scores
# logit- transform response
with(data1, plot(TchrTotal, log(SelfTotal / (25-SelfTotal) )))
with(data1, plot(Average_2019, log(SelfTotal / (25-SelfTotal) )))

# complementary loglog link, doesn't work
with(data1, plot(TchrTotal, log(-log(1 - (SelfTotal / 25)) )))
with(data1, plot(Average_2019, log(-log(1 - (SelfTotal / 25)) )))

# glm model w/ logit link, awaiting Faculty feedback on residuals
bm <- glm(cbind(SelfTotal, 25-SelfTotal)~TchrTotal + Average_2019, data=data1, family=binomial)
bm
summary(bm)
plot(bm)
```

### Not used: Utilizing dataset 2
session affects score, so we need to treat them separately (3 total models: data1, first, second)
```{r}
paired <- lm(SelfTotal ~ Average_2019 + TchrTotal + Session, data=data_paired)
summary(paired)
```

 data_paired: 1st session
```{r}
first <- data_paired[which(data_paired$Session=="First"),]
lm_first <- lm(SelfTotal ~ Average_2019 + TchrTotal, data=first)
summary(lm_first)
plot(lm_first)
```
Constant Variance assumption not met

 data_paired: 2nd session
```{r}
second <- data_paired[which(data_paired$Session=="Second"),]
lm_second <- lm(SelfTotal ~ Average_2019 + TchrTotal, data=second)
summary(lm_second)
plot(lm_second)
```
All assumptions met